The Right Way to Search Evolving Graphs

### 2016-02-20 paper.tex
add note for causality
add complexity analysis of algebraic BFS

\subsection{Description of the Algorithm}
\label{sec:descr-algor}

@@

@@

The blocked matrix--vector products introduced in the previous section allows us
to write down an elegant algebraic formulation of BFS on evolving graphs, as
presented in Algorithm~\ref{alg:bfsla}. Note that $\bm A_n^T$ need never be formed
explicitly, as only its matrix--vector product is required in the algorithm.

@@

>>>>

\subsection{Description of the BFS algorithm}
\label{sec:descr-algor}

@@

Note the edge set $E$ is $\cup_t\tilde E^{[t]} \cup E'$, which contains edges that
are causal structured.

@@

The blocked matrix--vector products introduced in the previous section allows us
to write down an elegant algebraic formulation of BFS on evolving graphs, as
presented in Algorithm~\ref{alg:bfsla}.

@@

\subsection{Computational complexity analysis of the algebraic BFS}
\label{sec:comp-compl-analys}

Given an evolving graph $G_n = \langle G^{[1]}, G^{[2]}, \ldots, G^{[n]} \rangle$, let $V$ be the set of active nodes,
$E = \cup_t \tilde E^{[t]} \cup E'$ be the set of edges, where
$\tilde E^{[t]}$ represents the set of edges of $G^{[t]}$ and $E'$ represents the set
of causal edges between time stamps. Let $\bm A_n$ be the corresponding
adjacency matrix of $G_n$.

Let's analyze the running time of Algorithm \ref{alg:bfsla}. 
Suppose $\bm A_n$ is dense.
Forming the block adjacency matrix $\bm A_n^T$ in line $3$
requires $\Theta(|V|^2)$ operations. 
We note, however, $\bm A_n^T$ need never be formed
explicitly, as only its matrix-vector product is required in the algorithm.
The matrix-vector product in line $7$ requires $O(|V|^2)$ operations.
In the worst case, we need to reach all active nodes and reach only one 
active node at each iteration. 
So the number of iterations $k$ of the while loop at line $6$ is bounded by
$|E|$, i.e., $k = \Theta(|E|)$. Hence, the total running time is 
$\Theta(|E||V|^2)$. This is much worse than Algorithm \ref{alg:bfs}, which
has linear running time.
